analysis

### 2019-12-04 01_Meta-analysis_experiments.Rmd
Save the experimental sites to a csv
Added some explaination and removed some old commented code

@@

* 2013  
   + Premer  
   + Milmerran   
   + Mt Mary   
   + Goolhi

@@

# source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
# ___ Datasets available ___
# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports

@@

glimpse(PM.dat)

@@

@@

leaflet(experiment_sites) %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   setView(lat = -27.31, lng = 150.456,zoom = 5) %>%
   addMarkers(lng = ~lon, lat = ~lat, popup = ~htmlEscape(location))
#   addPopups(lng = experiment_sites$lon, lat = experiment_sites$lat, popup = experiment_sites$location)

>>>>

This meta-analysis uses data collected by a number of researchers from the Department of Agriculture and Primary Industries and the University of Southern Queensland. It is worth noting Malcolm Riley and Dr Sue Thompsons effort in establishing and coordinating early field trials between 2010 and 2016.

@@

* 2013  
   + Premer  
   + Millmerran   
   + Mt Mary   
   + Goolhi

@@

@@

@@

## Powdery mildew ratings

   1. No powdery mildew colonies observed on any plant  
   2. Small colonies in lower 1/3 of canopy, up to 75% of plants affected  
   3. Colonies in lower 1/2 of canopy, >75% of plants affected  
   4. Colonies in lower 2/3 of canopy, up to 75% of plants affected  
   5. Colonies in lower 2/3 of canopy, >75% of plants affected  
   6. Colonies in lower 2/3 of canopy, 100% of plants affected  
   7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with colonies also in top 1/3 of canopy  
   8. Colonies to top of plant with >75% of plants affected  
   9. Colonies to top of plant with 100% of plants affected and heavy leaf drop

@@

write.csv(experiment_sites,"data/Mungbean_experiment_sites.csv", row.names = FALSE)

leaflet(experiment_sites) %>%
   addProviderTiles("Esri.WorldTopoMap") %>%
   setView(lat = -27.31, lng = 150.456,zoom = 5) %>%
   addMarkers(lng = ~lon, lat = ~lat, popup = ~htmlEscape(location))
